---
title: "Spatial Dynamics of Chinese Restaurant Ratings: Asian Density and Location Patterns in Maryland"
subtitle: "DSAN 6750 / PPOL 6805: GIS for Spatial Data Science"
authors:
  - name: Chen, Yihan; Deng, Liuting; Wang, Jiankun; Wang, Yongbo
    email: yc1140@georgetown.edu
    affiliation: Georgetown University
    corresponding: true
df-print: kable
title-block-banner: "#E69F0095"
title-block-banner-color: "black"
format:
  html:
    toc: true
    toc-depth: 3 
    df-print: kable
    math: true
    embed-resources: true
  pdf:
    # https://quarto.org/docs/reference/formats/pdf.html
    link-citations: true
    math: true
prefer-html: true
editor: 
  markdown: 
    wrap: 72
execute:
  warning: false
  message: false
---

## 1. Introduction

### 1.1 Background

Speaking of authentic Chinese food, places like the Bay Area in
California and Flushing in New York City often come to mind. These
regions, known for their vibrant Asian communities, boast many Chinese
restaurants that provide authentic flavors. In contrast, the DMV area
(D.C., Maryland, and Virginia) often falls short in this regard, with
Chinese cuisine that feels less connected to its roots. What are the
reasons behind this? One possibility lies in demographics---fewer Asian
residents across the region may contribute to a diminished demand for
authenticity. However, within the DMV, Maryland still stands out. It's
widely regarded as having better Chinese food compared to D.C. or
Virginia, likely because of its relatively larger Asian population.

From personal observations and countless taste tests (sadly), we
identify one pattern: the farther one ventures into areas with higher
concentrations of Asian residents, the more likely they are to stumble
upon a Chinese restaurant that serves dishes closer to the original
flavors. This could be attributed to clusters of Chinese communities,
which create a stronger demand for authentic food, coupled with cheaper
rent in suburban areas, allowing restaurants to focus on quality.

We are curious to explore whether this anecdotal pattern holds up to
statistics. Is there a measurable relationship between the density of
Asian residents and Chinese restaurant ratings? Moreover, are there
spatial clusters of high-rated restaurants, and does the presence of
these clusters create spillover effects, where one good restaurant
inspires the success of others nearby?

These questions have implications far beyond satisfying us, crazy
foodies, to find a better site in the DMV. For potential business
investors or restaurant owners, understanding these relationships could
guide strategic decisions about where to open new locations.

------------------------------------------------------------------------

### 1.2 Location Model (Economics)

The importance of locations in economics is demonstrated by two
prominent models: **Hotelling's Location Model** and **Salop's Circle
Model**, which explore the relationship between geography, consumer
behavior, and firm strategies.

#### 1.2.1 Hotelling's Location Model

> "In 1929, Hotelling developed a location model that demonstrates the
> relationship between location and pricing behavior of firms. He
> represented this notion through a line of fixed length. Assuming all
> consumers are identical (except for location) and consumers are evenly
> dispersed along the line, both the firms and consumers respond to
> changes in demand and the economic environment. Firms do not exercise
> variations in product characteristics; firms compete and price their
> products in only one dimension, geographic location. Therefore,
> traditional usage of this model should be used for consumers who
> perceive products to be perfect substitutes or as a foundation for
> modern location models."

For more details, see [this
website](https://en.wikipedia.org/wiki/Location_model_(economics)#Hotelling%27s_Location_Model).

Hotelling's model predicts that businesses should cluster in the middle
of a market to maximize their customer base. For example, in a linear
spatial market, if one restaurant exists in a neighborhood, a competing
restaurant might choose to locate directly next to it. This way, the
market splits into halves, with each business capturing customers on its
side.

This model assumes that businesses compete solely on geographic
location, with products being perfect substitutes. The idea parallels
the **Median Voter Theorem**, where competitors slightly undercut each
other until they meet equilibrium.

#### 1.2.2 Salop's Circle Model

> "Similar to the previous spatial representations, the circle model
> examines consumer preference with regards to geographic location.
> However, Salop introduces two significant factors: 1) firms are
> located around a circle with no endpoints, and 2) it allows the
> consumer to choose a second, heterogeneous good."

For more details, see [this
website](https://en.wikipedia.org/wiki/Location_model_(economics)#Salop's_Circle_Model).

The Salop model takes an opposing perspective. It proposes that
businesses should avoid clustering and instead space themselves to
maximize accessibility for the greatest number of consumers. It ensures
geographic diversity and minimal overlap in customer bases.

------------------------------------------------------------------------

### 1.3 Hypotheses

-   **Hypothesis 1**: Higher Asian population density is positively
    associated with Chinese restaurant ratings.
-   **Hypothesis 2**: High-rated Chinese restaurants exhibit spatial
    clustering.
-   **Hypothesis 3**: Spatial clustering of high-rated restaurants
    creates positive spillover effects on nearby establishments.

------------------------------------------------------------------------

## 2. Data and Methods

### 2.1 Data Source

The data for this study is sourced from two primary platforms:

-   **Point of Interest (POI) Data**:
    -   Chinese restaurant data in Maryland was collected using the
        Google Maps enrichment service provided by **Outscraper**.
    -   This dataset includes restaurant location details and ratings,
        with information updated for 2024.
-   **Demographic and Socioeconomic Data**:
    -   Data such as population and income were obtained from the U.S.
        Census Bureau's **American Community Survey (ACS)** 5-Year
        Estimates.
    -   The ACS data reflects information collected in 2022, the most
        recent survey year available.

------------------------------------------------------------------------

### 2.2 Data Cleaning

The following steps were taken to ensure alignment with the 2022
demographic data:

-   **Filtering by Year**:

    -   Restaurants that opened after 2022 were excluded to align with
        the available demographic data.

-   **Creating Asian Density Variable**:

    -   Using the merged data, a new variable, **Asian Density**, was
        created, calculated as:

$$
\text{Asian Density} = \frac{\text{Asian Population}}{\text{Total Population}}
$$

-   **Geographic Focus: Commuting Area**:

    -   A map of Chinese restaurant locations revealed a concentration
        in the **Washington, D.C.**, and **Baltimore metropolitan
        commuting areas**.
    -   Based on this observation, the dataset was refined to include
        only restaurants in these areas. The regions were defined using
        the **Office of Management and Budget (OMB)** standards for
        metropolitan and micropolitan areas.

------------------------------------------------------------------------

## 3. Exploratory Data Analysis

After cleaning, the main dataset was then converted into a spatial data
frame using longitude and latitude coordinates with the WGS 84
projection (CRS 4326). Maryland block group boundaries for 2022 were
retrieved. Both datasets were reprojected to a consistent CRS to ensure
spatial compatibility for our analysis.

### 3.1 Descriptive Statistics

```{r}
#| label: imports
#| code-fold: true
#| message: false
#| warning: false
#| echo: false
options(warn = -1)
suppressMessages({
  library(sp)
  library(sf)
  library(spdep)
  library(lmtest)
  library(sandwich)
  library(ggplot2)
  library(spatialreg)
  library(tmap)
  library(tigris)
  library(dplyr)
  library(tidyverse)
  library(leaflet)
  library(units)
  library(readxl)
  library(mapview)
})
```

```{r}
#| label: load-eda
#| code-fold: true
#| message: false
#| warning: false
#| echo: false
data <- read.csv("restaurant.csv")
data <- na.omit(data)

data_sf <- st_as_sf(data, coords = c("longitude", "latitude"), crs = 4326)
md_block_groups <- block_groups(state = "MD", year = 2022, progress_bar = FALSE)
md_block_groups <- st_transform(md_block_groups, crs = st_crs(data_sf))
data_sf <- st_transform(data_sf, crs = st_crs(md_block_groups))
```

#### 3.1.1 Restaurant and Rating

A histogram was generated to visualize the distribution of restaurant
ratings in Maryland.

Indeed, Maryland Chinese restaurants are generally well-rated. Most
Chinese restaurants have ratings concentrated between 3.5 and 4.5, with
a peak around 4.0. Ratings below 3.0 and above 4.5 are rare, following a
normal distribution.

```{r fig.height=5, fig.width=7}
#| label: plot restaurant
#| code-fold: true
#| message: false
#| warning: false
ggplot(data, aes(x = rating)) +
  geom_histogram(
    binwidth = 0.25, 
    fill = "#56B4E9", 
    color = "black"  
  ) +
  theme_classic() + 
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),  
    axis.title = element_text(size = 14),  
    axis.text = element_text(size = 12) 
  ) +
  labs(
    title = "Rating Distribution for Maryland Chinese Restaurants",
    x = "Rating",
    y = "Count"
  )
```

The map overlays restaurant data on Maryland block group boundaries,
with restaurants color-coded by their ratings.

It shows a clustering of restaurants in urbanized and suburban areas,
particularly around Baltimore and the D.C. metropolitan area. This
finding leads us to narrow down our restaurant dataset to a commuting
area in the later section. Ratings are distributed across locations,
with no clear trend of higher ratings clustering in specific regions.
Review counts vary significantly, with some restaurants attracting more
reviews than others.

```{r fig.height=5, fig.width=7}
#| label: Maryland Chinese Restaurants and Locations
#| code-fold: true
#| message: false
#| warning: false
data_with_coords <- data_sf %>%
  mutate(
    x = st_coordinates(.)[, 1], 
    y = st_coordinates(.)[, 2]
  )

ggplot() +
  geom_sf(data = md_block_groups, color = "gray60", fill = NA, size = 0.4) +
  geom_sf(data = data_sf, aes(color = as.factor(rating)), size = 2, alpha = 0.8) +
  geom_text(
    data = data_with_coords,
    aes(x = x, y = y, label = reviews),
    size = 3, vjust = -1, check_overlap = TRUE, color = "black"
  ) +
  labs(
    title = "Maryland Chinese Restaurants and Locations",
    color = "Rating"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"), 
    legend.title = element_text(size = 12),  
    legend.text = element_text(size = 10),   
    axis.text = element_blank(), 
    axis.title = element_blank(), 
    axis.ticks = element_blank(), 
    panel.grid = element_blank(),
    panel.background = element_blank() 
  )
```

#### 3.1.2 Asian Density

This graph displays the distribution of Asian density in Maryland. The
distribution is notably right-skewed, in the range from 0 to 0.5.

```{r fig.height=5, fig.width=7}
#| label: Asian Density Distribution in Maryland
#| code-fold: true
#| message: false
#| warning: false
ggplot(data, aes(x = AsianDensity)) +
  geom_histogram(
    binwidth = 0.05, 
    fill = "#009E73", 
    color = "black" 
  ) +
  theme_classic() +  
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),  
    axis.title = element_text(size = 14), 
    axis.text = element_text(size = 12) 
  ) +
  labs(
    title = "Asian Density Distribution in Maryland",
    x = "Asian Density",
    y = "Count"
  )
```

This presents a geographic visualization of average Asian density by
block group. Following the pattern revealed in the previous graph, we
used the scale from 0 to 0.5. The map shows that areas with higher Asian
density tend to be located in commuting zones, suggesting a trend where
the populations are concentrated in metropolitan areas.

```{r fig.height=5, fig.width=7}
#| label: Merged Asian Density by Block Group
#| code-fold: true
#| message: false
#| warning: false
asian_density_summary <- data_sf %>%
  st_drop_geometry() %>%
  group_by(GEOID) %>%
  summarize(AsianDensity = mean(AsianDensity, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(
    GEOID = as.character(GEOID),
    GEOID = str_pad(GEOID, width = 11, side = "left", pad = "0")
  )

md_block_groups_merged <- md_block_groups %>%
  left_join(asian_density_summary, by = "GEOID") %>%
  mutate(GEOID_prefix = substr(GEOID, 1, 9)) %>%
  group_by(GEOID_prefix) %>%
  summarize(
    geometry = st_union(geometry),  
    AsianDensity = mean(AsianDensity, na.rm = TRUE)
  )

ggplot(data = md_block_groups_merged) +
  geom_sf(aes(fill = AsianDensity), color = "gray80", size = 0.2) + 
  scale_fill_gradient(
    low = "white",
    high = "darkred",
    na.value = "white",
    limits = c(0, 0.5)
  ) +
  labs(
    fill = "Avg Asian Density\n(capped at 0.5)",
    title = "Merged Asian Density by Block Group"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),  
    legend.title = element_text(size = 12, face = "bold"), 
    legend.text = element_text(size = 10), 
    legend.key.size = unit(0.5, "cm"),  
    panel.grid = element_blank(), 
    panel.background = element_blank(), 
    axis.text = element_blank(), 
    axis.title = element_blank(), 
    axis.ticks = element_blank()  
  )

```

------------------------------------------------------------------------

### 3.2 Commuting Area

#### 3.2.1 Restaurant Locations in Commuting Area

This graph shows the restaurant locations within metropolitan areas,
with each blue dot representing a restaurant. The high concentration of
restaurants in the commuting area results from narrowing down the
original dataset by using the OMB standard to filter the restaurants in
metropolitan areas. This high concentration is advantageous for
regression analysis in the later part of the study.

```{r}
#| code-fold: true
#| message: false
#| warning: false
restaurant_data <- readxl::read_excel("filtered.xlsx")
restaurant_data <- na.omit(restaurant_data)

restaurant_sf <- st_as_sf(restaurant_data, coords = c("longitude", "latitude"), crs = 4326)

md_counties <- counties(state = "MD", year = 2022, class = "sf", progress_bar = FALSE)

counties_of_interest <- c("Montgomery", "Prince George's", "Calvert", "Charles", "St. Mary's",
                          "Baltimore city", "Anne Arundel", "Baltimore", "Carroll", "Harford",
                          "Howard", "Queen Anne's")

selected_counties <- md_counties[md_counties$NAME %in% counties_of_interest, ]

restaurant_sf <- st_transform(restaurant_sf, crs = st_crs(selected_counties))
selected_counties <- st_transform(selected_counties, crs = st_crs(restaurant_sf))

restaurant_sf_cropped <- st_intersection(restaurant_sf, st_union(selected_counties))

maryland_block_groups <- block_groups(state = "MD", year = 2022, progress_bar = FALSE)

asian_density_summary <- restaurant_data %>%
  group_by(GEOID) %>%
  summarize(AsianDensity = mean(`AsianPopulation` / `TotalPopulation`, na.rm = TRUE))

maryland_block_groups <- maryland_block_groups %>%
  mutate(GEOID = as.character(GEOID)) %>%
  left_join(asian_density_summary, by = "GEOID")

maryland_block_groups <- st_transform(maryland_block_groups, crs = st_crs(selected_counties))
maryland_block_groups_cropped <- st_intersection(maryland_block_groups, st_union(selected_counties))
```

```{r fig.height=5, fig.width=7}
#| code-fold: true
#| message: false
#| warning: false
ggplot() +
  geom_sf(data = selected_counties, fill = "white", color = "gray60", size = 0.3) +
  geom_sf(data = restaurant_sf_cropped, color = "#56B4E9", size = 2, alpha = 0.35) +
  labs(
    title = "Restaurant Locations in Washington-Baltimore Corridor",
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"), 
    plot.caption = element_text(size = 10, hjust = 1, face = "italic"), 
    panel.grid = element_blank(), 
    panel.background = element_blank(),  
    legend.position = "none",  
  )
```

We also present it with the mapview package.

```{r fig.height=5, fig.width=7}
#| code-fold: true
#| message: false
#| warning: false
mapview(selected_counties, color = "gray", alpha = 0.3) + 
  mapview(
    restaurant_sf_cropped,
    zcol = "rating",                     
    col.regions = colorRampPalette(c("#56B4E9", "#E69F00", "#D55E00"))(100),  
    cex = 4,                             
    alpha = 0.7                          
  )
```

#### 3.2.2 Asian Density in Commuting Area

This displays Asian density by block group based on a narrowed-down
dataset. It clearly shows that higher Asian density is concentrated in
the Washington, D.C., and Baltimore commuting areas.

```{r fig.height=5, fig.width=7}
#| code-fold: true
#| message: false
#| warning: false
maryland_block_groups_merged <- maryland_block_groups_cropped %>%
  mutate(GEOID_prefix = substr(GEOID, 1, 10)) %>% 
  group_by(GEOID_prefix) %>%
  summarize(
    geometry = st_combine(geometry),           
    AsianDensity = mean(AsianDensity, na.rm = TRUE)  
  )

asian_density_map <- ggplot(data = maryland_block_groups_merged) +
  geom_sf(aes(fill = AsianDensity), color = "gray80", size = 0.2) +  
  scale_fill_gradient(
    low = "white",
    high = "darkred",
    na.value = "white",
    limits = c(0, 0.5)
  ) +
  labs(
    fill = "Avg Asian Density\n(capped at 0.5)",
    title = "Asian Density by Block Group"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold"),  
    legend.title = element_text(size = 12, face = "bold"),  
    legend.text = element_text(size = 10), 
    legend.key.size = unit(0.5, "cm"), 
    panel.grid = element_blank(),  
    panel.background = element_blank(), 
    axis.text = element_blank(),  
    axis.title = element_blank(),  
    axis.ticks = element_blank()   
  )

print(asian_density_map)

```

------------------------------------------------------------------------

## 4. Spacial Analysis

Before investigating the relevance of spatial effects in our hypothesis,
let's try a non-spatial regression model: it may simply be that the
spatial autocorrelation in rating of restaurants is entirely explained
by the Asian density in Maryland.

### 4.1 Regression Analysis (OLS)

To investigate whether the ratings of Chinese restaurants in Maryland
are influenced by local demographic and socioeconomic factors, we fit a
"standard" OLS model to estimate the variables of our interests:

$$
\text{Rating}_i = \beta_0 + \beta_1 \cdot \text{AsianDensity}_i + \beta_2 \cdot \text{MedianHouseIncome}_i + \beta_3 \cdot \text{PublicTransport}_i + \epsilon_i
$$

```{r}
#| code-fold: true
#| message: false
#| warning: false
asian_density_summary <- asian_density_summary %>%
  mutate(GEOID = as.character(GEOID))

restaurant_data <- restaurant_data %>%
  mutate(GEOID = as.character(GEOID)) %>%
  left_join(asian_density_summary, by = "GEOID")

```

```{r}
#| code-fold: true
#| message: false
#| warning: false
ols_model <- lm(rating ~ AsianDensity + MedianHouseholdIncome + PublicTransportationCommuters , 
                data = restaurant_data)
summary(ols_model)
```

Higher Asian population density positively influences restaurant ratings
(p = 0.0164). But median household income and the number of public
transport commuters in the OLS model are insignificant.

```{r fig.height=5, fig.width=7}
#| code-fold: true
#| message: false
#| warning: false
residuals <- resid(ols_model)
fitted_values <- fitted(ols_model)


ggplot(data = data.frame(fitted_values, residuals), aes(x = fitted_values, y = residuals)) +
  geom_point(color = "#D55E00", alpha = 0.7) + 
  geom_hline(yintercept = 0, color = "#0072B2", linetype = "dashed", size = 0.8) +
  labs(
    title = "Residuals vs. Fitted Values", 
    x = "Fitted Values", 
    y = "Residuals"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"), 
    axis.title = element_text(size = 12),  
    axis.text = element_text(size = 10) 
  )
```

We create a scatter plot of residuals vs. fitted values to assess the
OLS model's fit and residual distribution. The residuals, derived from
the model, are evenly distributed around a zero line with no clear
patterns, indicating a good fit. But we are still curious if residuals
from OLS estimation exhibit a relationship, due to spatial
autocorrelation with tools.

------------------------------------------------------------------------

### 4.2 Spacial Residual (Moran's I)

Moran's ð¼ is used to test if our error terms are independent of the
spatial distribution.

To define neighbors for Moran's ð¼, a spatial weights matrix is used to
represent relationships between restaurants. Neighbors are defined using
5 nearest neighbors, linking each restaurant to its five closest
neighbors by geographical coordinates.

```{r}
#| code-fold: true
#| message: false
#| warning: false
restaurant_sf <- st_as_sf(restaurant_data, coords = c("longitude", "latitude"), crs = 4326)
coords <- st_coordinates(restaurant_sf)
k_nb <- knn2nb(knearneigh(coords, k =5))
listw_k <- nb2listw(k_nb, style = "W")
```

```{r}
#| code-fold: true
#| message: false
#| warning: false
moran_rating <- moran.test(restaurant_sf$rating, listw_k)
print(moran_rating)

ols_model <- lm(rating ~ AsianDensity + MedianHouseholdIncome + PublicTransportationCommuters, 
                data = restaurant_data)
residuals_ols <- resid(ols_model)

moran_residuals <- moran.test(residuals_ols, listw_k)
print(moran_residuals)
```

For restaurant ratings, Moran's ð¼ = 0.0605 (p = 0.0071) indicates
significant positive spatial autocorrelation, suggesting clustering of
high and low ratings. However, for regression residuals, Moran's ð¼ =
0.0338 (p = 0.0809) shows weaker spatial autocorrelation.

```{r fig.height=5, fig.width=7}
#| code-fold: true
#| message: false
#| warning: false
moran_lag <- lag.listw(listw_k, restaurant_sf$rating)

moran_data <- data.frame(
  rating = restaurant_sf$rating,                    
  spatial_lag = moran_lag                           
)


moran_data <- moran_data %>%
  mutate(
    rating_std = scale(rating, center = TRUE, scale = TRUE),      
    spatial_lag_std = scale(spatial_lag, center = TRUE, scale = TRUE) 
  )


moran_scatterplot <- ggplot(moran_data, aes(x = rating_std, y = spatial_lag_std)) +
  geom_point(color = "#D55E00", alpha = 0.7) +              
  geom_smooth(method = "lm", color = "#0072B2", se = FALSE) + 
  labs(
    title = "Moran's I Scatterplot",
    x = "Standardized Rating",
    y = "Spatial Lag of Standardized Rating"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),  
    axis.title = element_text(size = 12),  
    axis.text = element_text(size = 10)   
  )

print(moran_scatterplot)
```

------------------------------------------------------------------------

### 4.3 Spacial Regression (SAR)

The spacial autocorrelation is significant and the residual
autorrelation is not significant, which explains the spacial
correlation. But we still try to include an additional spatial
regression (SAR).

```{r}
#| code-fold: true
#| message: false
#| warning: false
sem_model <- lagsarlm(rating ~ AsianDensity , 
                        data = restaurant_sf, 
                        listw = listw_k)
summary(sem_model)
```

The spatial regression shows that Asian population density indeed
significantly impacts restaurant ratings. In addition, the spatial lag
coefficient (Rho) is 0.1133 (p = 0.092). It only shows a limited spacial
independence.

------------------------------------------------------------------------

## 5. Discussion

### 5.1 Main Findings

Our result shows that the higher Asian population density positively
affects Chinese restaurant ratings. Also, high-rated Chinese restaurants
exhibit spatial clustering. However, the spatial clustering of
high-rated restaurants does not create spillover effects on nearby
establishments.

------------------------------------------------------------------------

### 5.2 Interpretation of Result

#### 5.2.1 Support for Hotelling's Model

In the DMV area, the data suggests some level of clustering. High-rated
Chinese restaurants tend to appear near others, aligning partially with
Hotelling's idea of businesses grouping to share the market demand
efficiently.

However, our finding of no significant spatial spillover effects
indicates that the new restaurant's presence doesn't detract from the
ratings of the existing restaurant. This suggests sufficient demand in
the market for both restaurants, supporting Hotelling's idea that
businesses can coexist and compete successfully in proximity.

#### 5.2.2 Departure from Salop's Model

Our findings don't align strongly with Salop's model because clustering
occurs rather than spacing out. And the lack of a strong spillover
effect from proximity further challenges Salop's prediction.

#### 5.2.3 A Potential Third Framework

The lack of negative spillover effects and the persistence of clustering
may indicate a "sufficient demand" scenario. In this case, clustering is
sustainable because the density of demand (in areas with higher Asian
populations) can support multiple businesses. This finding could
contrast with markets like Flushing, NY, where high demand might already
be saturated, and adding a new business could lead to a redistribution
of customers or a drop in ratings.

------------------------------------------------------------------------

### 5.3 Limitation and Future Directions

Our dataset only contains Maryland residents, and it can be more
interesting to investigate whether the no spillover effect holds in
other regions, such as the Bay Area or Flushing, where the Asian
population density is much higher. Besides, it can be analyzed how this
pattern changes with varying levels of restaurant quality, as
lower-rated restaurants may face stronger competition effects than
higher-rated ones.

------------------------------------------------------------------------

## 6. Conclusion

Our evidence finds that Asian density significantly and positively
affects Chinese restaurant ratings.
